### 2022-12-05 dissertation/chapters/08-results.tex
🐛 (derived-publications): Removed redundant entries and small technical fix

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{\index{heuristic}heuristic selection probabilities}. Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively. Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

>>>>

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichlet probability distribution}Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{\index{heuristic}heuristic selection probabilities}. Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively. Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.
